---
output:
  html_document:
    df_print: paged
permalink: /research/
---

```{r setup, echo = FALSE}
library(knitr)
```

:::: {style="display: grid; grid-template-columns: 4fr 1fr 8fr 2fr; grid-column-gap: 20px"}

::: {}

```{r child ='leftside.Rmd'}
```

:::

::: {}

:::



::: {}

---

#### [Home](https://john-p-ryan.github.io/) | [**Research**](https://john-p-ryan.github.io/research.html) | [CV](https://john-p-ryan.github.io/files/CV.pdf)

---

### Publications

["Debias Random Forest Regression Predictors"](https://www.researchgate.net/publication/372239538_Debias_random_forest_regression_predictors), 2023   
With Lihua Chen and Prabhashi Withana Gamage   
Published in Journal of Statistical Research

---

### Presentations
"Debias Random Forest Regression Predictors", 2021   
Math Fest 2021, presenting author   
[See slides](https://drive.google.com/file/d/1l_N-IQXZizEg0v_7TLgmmJkye2bsWx_E/view?usp=sharing)


"Inferring the Preferences of Presidential Candidates from Their Tax Policy Proposals", 2022  
Discover USC 2022, poster session honorable mention

---

### Other projects
"Inferring the Preferences of Presidential Candidates from Their Tax Policy Proposals", 2022   
Senior thesis, with Jason DeBacker  
Work in progress   
[See repo](https://github.com/PSLmodels/InverseOptimalTax/tree/main)

"Mathematical Foundations of Data Science, Optimal Transport", 2022   
NSF REU project under Wuchen Li, UofSC Math   
[See slides](https://drive.google.com/file/d/1d0LliYPvpbVtJaj47LBw7l_bA67IcCOh/view?usp=sharing)


:::

::::