---
output:
  html_document:
    df_print: paged
---

```{r setup, echo = FALSE}
library(knitr)
```

:::: {style="display: grid; grid-template-columns: 4fr 1fr 8fr 2fr; grid-column-gap: 20px"}

::: {}

```{r child ='leftside.Rmd'}
```

:::

::: {}

:::



::: {}

---

#### [**Home**](john-p-ryan.github.io) | [Research](https://john-p-ryan.github.io/research/) | [CV](https://john-p-ryan.github.io/Ryan_CV_jul23.pdf)

---

### Welcome!

My name is John Ryan and I am a second year PhD student in economics at the University of Wisconsin - Madison, originally from Charleston, SC. 

My interests lie in public finance, computational methods, and macroeconomics. My previous work includes open source modeling for [Inverse-Optimal Tax methods](https://github.com/PSLmodels/InverseOptimalTax/tree/main), and [reducing bias for machine learning estimators](https://www.banglajol.info/index.php/JStR/article/view/67466/45250). 

Before starting my PhD, I completed my BS in Economics, Mathematics and Statistics at the University of South Carolina (the real USC). Go Gamecocks!

Feel free to contact me by email at [john.p.ryan@wisc.edu](mailto:john.p.ryan@wisc.edu) if you have any questions.

---

### Posts

[7/22/23: My first paper was published in the Journal of Statistical Research](https://john-p-ryan.github.io/jekyll/update/2023/07/22/first-paper-published)

[6/23/23: I passed my prelims!](https://john-p-ryan.github.io/jekyll/update/2023/06/23/I-passed-my-prelims!)


:::

::::